Transforming Trash as an Artistic Act

### 2015-11-10 main.tex
Re-organization, arguments related with culture.
Former-commit-id: 9e4e0547cdc0f21b97a0681bcd3c44d5187f075b

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
\usepackage{epigraph}
%\usepackage{setspace}
%\doublespacing
\usepackage{graphicx}
%\graphicspath{ {graphics/} }
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[titletoc]{appendix}
%\usepackage{chngcntr}

%\counterwithout{figure}{chapter}

@@

% Quotation command
\providecommand{\quotes}[1]{``#1''}
\providecommand{\singlequotes}[1]{`#1'}

@@

%****************************************
% Title Ideas for Thesis 
% - Trash as an Artistic Medium
% - Trash Notebooks: Trash in the Context of Art
% - Trash Notebooks: Exploring the potential of trash through art practice
% - Notebooks from Trash
% - Transforming Trash as an Artistic Act
%........................................

@@

%\title{Transforming Trash as an Artistic Act}
%\author{Mustafa İlhan}
%\maketitle

@@

@@

\selectlanguage{turkish}
%****************************************
% TURKISH
\begin{abstract}

% Ne, Nasıl, Sonuç.

% Sanatta çöpün yeri inceleniyor, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir. Ya da en azından proje kapsamında üretilen işin. Ya da bu bağlamda ele alınabileceği iddia edilmektedir.

Bu çalışmanın amacı çöpü dönüştürmenin sanat ve sanatsal eylem bağlamında tartışmaktır. Çöpün kültürel ve kuramsal olarak nasıl ele alındığı araştırılmıştır. Çöpü dönüştürmenin nasıl ne ne şekilde mümkün olduğu incelenmiştir. Sanatsal üretim yöntemi olarak çöpü (tercih etmiş)kullanan sanatçıların yaklaşımları ele alınmıştır. Neden ve nasıl atıkları sanat işlerinde ve eylemlerinde kullandıkları sorgulanmıştır ve bunun toplumsal ve teorik olarak nereye oturduğu/ne anlama geldiği/nasıl anlaşılabileceği incelenmiştir.

% Tez dahilinde geliştirilen proje ile çöpten dönüştürülmüş defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır. Farklı zaman ve mekanlardan toplanan kağıtlar birbirinden farklı kompozisyonlar oluşturmakta ve endüstriyel defterlere alternatif oluşturmaktadır. Aynı zamanda bu defter hakim sistemin dışındaki mekanlarda bulunarak (kamusal ortak alan)

% Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir. Beraberinde pek çok akım ve üretim biçimini tetiklemiştir. Hem sanatın dili genişledi hem de objelerin sanat için farklı anlamlarda ve amaçlarla kullanılmaya başladı. Bu çalışmda çöpün sanatsal bağlamda ele alınması yapılacaktır. Çöpü daha iyi anlayabilmek için throw away. Çöpün nasıl sanatta yer bulduğu incelenmiştir. ve aynı zamanda aslında çöpün ne olduğu sorgulanmıştır.

Çöp ve sanatsal eylem birlikte alınarak incelenmiştir. Çöp olgusu ve sanat dışı malzemelerin sanatta kullanılması sorgulanmıştır. Teoriler ve methodlar ele alınmıştır. Çöpün ne olduğu sorgulanmaktadır.

>>>>

\documentclass[12pt]{report}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[turkish,english,shorthands=:!]{babel}
\usepackage{apacite}
\usepackage[a4paper,width=155mm,top=25mm,bottom=25mm]{geometry}
\usepackage{epigraph}
\usepackage{graphicx}
%\graphicspath{ {graphics/} }
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{wrapfig}
\usepackage[usenames, dvipsnames]{color}
\usepackage[titletoc]{appendix}

%\usepackage{chngcntr}
%\counterwithout{figure}{chapter}

%\usepackage{setspace}
%\doublespacing

@@

\providecommand{\quotes}[1]{``#1''}
\providecommand{\singlequotes}[1]{`#1'}
\providecommand{\todo}[1]{\textcolor{red}{#1}}
\providecommand{\comment}[1]{\textcolor{cyan}{#1}}
\providecommand{\paraphrase}[1]{\textcolor{magenta}{#1}}

@@

%****************************************
% Title Ideas for Thesis 
% - Trash as an Artistic Medium
% - Notebooks from Trash: Trash in the Context of Art
% - Notebooks from Trash: Exploring the potential of trash through art practice
% - Transforming Trash as an Artistic Act
% - Act of Transforming Trash in the Context of Art
%........................................

@@

@@

% The aim of this thesis is to investigate the theories and methodologies of type design within the context of ideology. // The purpose of this thesis is to explore the transformation of discarded items through the artistic methodologies (or in the context of art). It is questioned the role of art in transformation of discarded items. This thesis follows the discussions of what is waste and the states of waste or meaning of waste. Within this thesis the project transformed the collected discarded items and then later spreads them to the community again.

@@

\selectlanguage{turkish}
%****************************************
% TURKISH
\begin{abstract}
\comment{Sanatta çöpün yeri incelenip, çöpü dönüştürmenin bir sanatsal eylem olduğu iddia edilmektedir. Ya da en azından proje kapsamında üretilen işin. Ya da bu bağlamda ele alınabileceği iddia edilmektedir.}

Bu çalışmanın amacı çöpü dönüştürmenin sanat ve sanatsal eylem bağlamında tartışmaktır. Çöpün kültürel ve kuramsal olarak nasıl ele alındığı araştırılmıştır. Çöpü dönüştürmenin nasıl ne ne şekilde mümkün olduğu incelenmiştir. Sanatsal üretim yöntemi olarak çöpü (tercih eden) kullanan sanatçıların yaklaşımları ele alınmıştır. Neden ve nasıl atıkları sanat işlerinde ve eylemlerinde kullandıkları sorgulanmıştır ve bunun toplumsal ve teorik olarak nereye oturduğu/ne anlama geldiği/nasıl anlaşılabileceği incelenmiştir.

\comment{Tez dahilinde geliştirilen proje ile çöpten dönüştürülmüş defterler ile çöpe bakış açısının dönüştürülmesi amaçlanmıştır. Farklı zaman ve mekanlardan toplanan kağıtlar birbirinden farklı kompozisyonlar oluşturmakta ve endüstriyel defterlere alternatif oluşturmaktadır. Bu defter hakim sistemin dışındaki mekanlarda konulmuştur. (kamusal ortak alan)}

\comment{Sanat dışı objelerin sanata malzeme olması sanatın dilinde genişlemere olanak vermiştir. Beraberinde pek çok akım ve üretim biçimini tetiklemiştir. Hem sanatın dili genişledi hem de objeler sanat için farklı anlamlarda ve amaçlarla kullanılmaya başladı. Bu çalışmda çöpün sanatsal bağlamda ele alınması yapılacaktır. Çöpün nasıl sanatta yer bulduğu incelenmiştir.}

Çöp ve sanatsal eylem birlikte alınarak incelenmiştir. Çöp olgusu ve sanat dışı malzemelerin sanatta kullanılması sorgulanmıştır. Teoriler ve methodlar ele alınmıştır. Çöpün ne olduğu sorgulanmaktadır ve çöpe yeni bir bakış açısı kandırılmak amaçlandırılmaktadır.

### 2015-11-10 uncategorized.tex
lots of comment, new artworks
Former-commit-id: 434f20e9a098218eeb84ceeb22620f30c4095721
Re-organization, arguments related with culture.
Former-commit-id: 9e4e0547cdc0f21b97a0681bcd3c44d5187f075b

% FROM http://stanforddailyarchive.com/cgi-bin/stanford?a=d&d=stanford19920130-01.2.5&e=-------en-20--1--txt-txIN-------#
% The thing to do is to find some way --- and it can be done, I think, through art --- to enjoy life in its vast multiplicity. --- John Cage

% FROM Wild Art
% Bu epigraphta aslında şöyle bir sıkıntı var, bir şeyin miktarı artınca daha fazla insanın onun üzerinde düşeceğini varsaymak biraz sıkıntı olabilir.
% We are going to make a lot more junk, and there is going to be a lot more junk art. I think people are going to have a lot to say about it, and more people need to think about it. --- Jeremy Mayer, quote taken from American Craft Magazine, December/January 2011.

@@

%%
%%
\subsection{What is trash?}
In this thesis work to understand the different aspects of trash is a key element. Because as scholars agreed on (ref required.) it is part of our life and daily practice and it is very common concepts from developed western societies to rural areas, from disaster areas to \ldots(something beautiful here). Sometimes it is accepted as a problem that is need to carefully and seriously manged. On the other hand it is accepted as a source of diversity. (To establish a solid understanding for trash, it is important to see its dilemmas (it is really a dilemma?)). Therefore we should ask these questions: What is trash? How does it became trash? Is it a end product or a source material? How much is it valuable? How much is it dangerous?

%%
%%
\subsection{Trash is everywhere and, produced every time}
Modern (developed) societies are continuously generating trash and, pile them on landfills. It's a common object category that all people share its possession. During daily activities trash is generated and people get rid of them by throwing away. (Various objects become trash after their primary functions daily. Who defined the primary function? Primary function is the only function. People cares the package of the objects that they buy. They buy the coffee not the cup of it. After coffee finished the life of cup also finishes. There is a lifetime defined (or forecast) by the producer of objects. However it is not bound to the producer, also consumer play an important role. There are different choices. Throw it away. Keep it. Give it. Mostly wining choice is throwing away and by the result of it mountains of garbage are increasing.) The vast amount of industrial discarded items spread through the landfills to oceans. They are the result of highly complex industrial production methods. They are not easily disposable items. They live in the nature thousands of years. Most of them packages that are used to carry or protect other materials. After real material used these packages became valueless (or useless). (types of trash can be mentioned here, but currently in the artwork I'm using paper packages, therefore, it is more important.) How manage the all this increasing trash that damaging nature?  This is the common approach to trash and the main problem. (actually the sustainability problem.) It is not the only problem, It can be thought that it is a losing the ability to transform new things, alternative behaviors etc. (Instead of creating new opportunities or alternatives, it is a consuming all them and producing huge pile of trash.) (reference Zizek idealization of nature, to love nature is to love trash. Live with trash. Do not see it as trash actually. Then the question is how to love trash? how to live with trash? can living with our trash enrich (our perceptions, abilities)? how not to see them as trash and useless? Can it be possible with art?)

% TODO PRAP. REF.
Waste pickers are an important part of the story in Latin America, as more is being thrown away than ever. The World Bank estimates that the amount of solid waste generated in cities is growing faster than the rate of urbanization. The higher the income level and the rate of urbanization, the greater the amount of solid waste produced. OECD countries produce almost half of the world’s waste. Africa and South Asia produce the least waste. High-income countries have the highest collection rates and are most likely to dispose of waste to landfills or incinerators. Low-income countries have the lowest collection rates and are most likely to dispose of their waste in open dumps. However, low-income countries also have the largest numbers of informal waste pickers who collect, sort, and reclaim recyclables---thus reducing costs to the city and to the environment. (FROM Trash as Treasure, BY WILLIAM L. FASH AND E. WYLLYS ANDREWS)

% TODO PRAP. REF.
Literature is recycled material, a pretext for making more art. I learned this distillation of lots of literary criticism in workshops with children. I also learned that creative and critical thinking are practically the same faculty, since both take a distance from found material and turn it into stuff for interpretation. For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress. (FROM Recycle the Classics, BY DORIS SOMMER)

% From Beautiful Trash Art and Transformation BY PAOLA IBARRA ReVista
% TODO PRAP. REF.
We relate to garbage daily. We use it, produce it and dispose of it. Endlessly. The most obsessive of us get rid of it as fast as we can. The hoarder likes to salvage a few things for later use---the plastic and glass containers, the cardboard boxes. We know that capitalism’s escalating cycles of production, consumption and obsolescence keep worsening an already problematic relationship between humankind, waste and nature (not to mention social and economic relations). Despite a relatively increased awareness about consumption and its consequences, the pace at which we also acquire and dispose of material objects is exploding. Particularly in the connection between garbage and the arts, I am interested in two questions. First, the issue of recycling as a general practice in the arts; and secondly, in the whole issue of representation---that is, representation of waste as subject, and representation (of waste or others subjects) through waste as material. (BY PAOLA IBARRA)

%%
%%
\subsection{Cycle of trash}
Trash moves, objects moves from place to place. From homes to garbage trucks. From streets to land fills. From garbage baskets to sculptures. [REF. MIT Garbage project] Lots of different people touches to trash. With the trash what moves?

@@

%%
%%
\subsection{How does it become trash?}
Here the purpose is to understand the dynamics that turn objects to trash. By understanding them is provide a roadmap (or ideas) how to turn trash to something valuable? (The purpose of this thesis is to find (or explore) a way(methodology, approach) to add value to object using artistic methods? Therefore first question is why they are less-valued, and ignored. How to make them valuable? How to make them part of our life again?)

@@

%%
%%
\subsection{Garbology}
Garbology is a study of waste as a social science.

@@

% Binding things together and separating things from each other.

@@

%%
%% TODO sample statements here.
\subsection{Artist statements}
\begin{itemize}
\item I am an artist living in New York City, and my experience of daily life here is both the catalyst for and the subject of my art. Working from the local, the personal and the ordinary - the paper take-out coffee cup in the palm of my hand, the view from my studio window in the Garment District, friends and their children, the community garden around the corner from my apartment in Hell's Kitchen - my drawings, paintings and installations are about what happens when the familiar suddenly undergoes a perspective shift and is revealed in all its wonder and infinite possibility. With this shift, mundane things become extraordinary, as nodes of rapidly expanding sets of connections, relationships and new artworks.

My approach to art-making is both observational and process-oriented. A fascination with cultural, physical and temporal change combined with the possibility of infinite variation unify projects as diverse as drawing and painting on my used coffee cups each day, repeatedly recording the view from my studio in paint and photography over the course of six years, depicting in two and three dimensions the incursion of human activity on the fractal meanders of salt marshes along the New Jersey coast, and painting portraits of alternative families in my New York City neighborhood. (from http://gwynethleech.com/)
\end{itemize}

%%
%% ACTIVISM as a methodology 
%% TODO reading...
\subsection{Art and activism}
Using trash in the art has some critical messages to societies and authorities. Especially in the trash case there is a activist(political) act.

%*************************************
% Phrases...
% What specific social issues are you trying to address through Labyrinth?
% In view of the diversity of online crowdsourced art projects, as illustrated by the examples cited so far, it is useful to map out this artistic trend by developing a comprehensive and multidimensional typology of online crowdsourced art. Table 1 organizes this classification according to a set of multiple criteria. (But this one can be used at introduction, but it is too long to fit on introduction. Maybe select works by giving prominence to some of the features. So the approach to the trash is going to be introduced and also it is reveals the what i am doing in this context.) (A Typology of Online Crowdsourced Art. Diye bir örnek var aslında benzer bir şekilde bu trash içinde yapılabilir.) 
\subsection{Crowdsourcing, Participation}
% TODO needs reference, FROM Crowdsourced Art and Collective Creativity
In the words of Jeff Howe (2006b), the Wired columnist who coined this term in June 2006, \quotes{crowdsourcing represents the act of a company or institution taking a function once performed by employees and outsourcing it to an undefined (and generally large) network of people in the form of an open call}. The vital elements that qualify an outreach strategy as crowdsourcing are, according to Howe, the use of the open call format and the reliance on a large network of potential workers. Although in some cases there is a material reward for the best contributions, the existence of financial incentives is not a required feature in crowdsourcing. Because of the diversity of its applications, crowdsourcing continues to be a disputed term in both the scholarly literature and the popular press; Howe’s original definition is, in this sense, a helpful delineation of its practical sphere.

@@

% why collaboration, is it really a collaboration?

% TODO 
% Umberto Eco's Open Work

% Not all artist transform trash although some deconstruct them. Michael Landy is one of them. 
% Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers. Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part. Reveal all his possessions. and loosing them while you are alive. Turning them to rubbish making them unusable. breaking down the all the meaning. breaking down the connections. 
% Michael Landy's Art Bin uses a art gallery to create his dust bin. Describing the work, simply called Art Bin, as 'about failure', Landy is inviting members of the public to bring their own artistic failures along to the gallery from 29 January, where their worthlessness will be assessed. Damien Hirst, Gillian Wearing, Tracey Emin and Mark Titchner have already contributed, offering sculptures, paintings and prints. "There's no hierarchy once they are in the bin" All of them are accepted as same. Ultimate equality. Tosing them to the dust bin makes them rubbish even if they are combined from failed attempts. Nothing's too good for the art bin. Everything can fit into the art bin. Michael Landy transforms the SLG into Art Bin, a container for the disposal of works of art. As people discard their art works the enormous 600m³ bin becomes, in Michael Landy’s words, “a monument to creative failure”. It is a very big glass bin and isolates people. There is a provocative approach to the art and art objects by saying that "Nothing's too good for the art bin". There is no limitation of throwing away even if art.

% In this thesis project case the issue is not the language of art and its methods.

>>>>

@@

% TODO PRAP. REF.
% Ne diyor?
Literature is recycled material, a pretext for making more art. I learned this distillation of lots of literary criticism in workshops with children. I also learned that creative and critical thinking are practically the same faculty, since both take a distance from found material and turn it into stuff for interpretation. For a teacher of literature over a long lifetime, these are embarrassingly basic lessons to be learning so late, but I report them here for anyone who wants to save time and stress. (FROM Recycle the Classics, BY DORIS SOMMER)

%%
%%
\subsection{Cycle of trash}

@@

@@

%%
%%
\subsection{Garbology}
Garbology is a study of waste as a social science. applying methodologies of archeology to the human debris.

@@

@@

%*************************************
% Phrases...
% What specific social issues are you trying to address through Labyrinth?
% In view of the diversity of online crowdsourced art projects, as illustrated by the examples cited so far, it is useful to map out this artistic trend by developing a comprehensive and multidimensional typology of online crowdsourced art. Table 1 organizes this classification according to a set of multiple criteria. (But this one can be used at introduction, but it is too long to fit on introduction. Maybe select works by giving prominence to some of the features. So the approach to the trash is going to be introduced and also it is reveals the what i am doing in this context.) (A Typology of Online Crowdsourced Art. Diye bir örnek var aslında benzer bir şekilde bu trash içinde yapılabilir.) 
\subsection{Crowdsourcing, Participation, Open Work}
% TODO needs reference, FROM Crowdsourced Art and Collective Creativity
In the words of Jeff Howe (2006b), the Wired columnist who coined this term in June 2006, \quotes{crowdsourcing represents the act of a company or institution taking a function once performed by employees and outsourcing it to an undefined (and generally large) network of people in the form of an open call}. The vital elements that qualify an outreach strategy as crowdsourcing are, according to Howe, the use of the open call format and the reliance on a large network of potential workers. Although in some cases there is a material reward for the best contributions, the existence of financial incentives is not a required feature in crowdsourcing. Because of the diversity of its applications, crowdsourcing continues to be a disputed term in both the scholarly literature and the popular press; Howe’s original definition is, in this sense, a helpful delineation of its practical sphere.

@@

% why collaboration, is it really a collaboration? It is methodology used in my practice.

% TODO: Umberto Eco's Open Work

%*************************************
% ARTWORKS:
% Not all artist transform trash although some deconstruct them. Michael Landy is one of them. Michael Landy's Break Down Inventory is a two week show / display of destruction process of his all possessions on a dissemble line with the help of 10 workers. Firstly they are classified and recorded for three years and the deconstructed in two weeks by separating every element to the smallest part. Reveal all his possessions. and loosing them while you are alive. Turning them to rubbish making them unusable. breaking down the all the meaning. breaking down the connections. 
%.....................................

%*************************************
% Solid claims about its cultural aspect.
\subsection{Book: Recycled, Re-Seen: Folk Art from the Global Scrap Heap}

All of them must be paraphrased. Establish connection with the other sections.

\comment{Notes from the book.} They also choose the word recycle. (It is hard to say that they use it wrongly, but what they refer is actually upcycling. Creative reuse, inventing new things from discard.)

They also states that the practice of tribal people artfully transform Coca-Cola bottle (given as example by the authors). From western trash to tribal treasure. \paraphrase{For the Kalahari Bushmen, the process appears to be one not so much of reusing but of creating anew; not so much transforming, a inventing (p.9).} It stated these found objects is accepted as a gift from gods. A disposable item becomes imminent desire and profound social consequence. (Intercultural recycling.) \paraphrase{Both presentations tell a story about an aesthetic and cross-cultural process --- as well as an economic and political one --- which is defined by the act of recovering and transforming the detritus of the industrial age into handmade objects of renewed meaning, utility, devotion, and sometimes arresting beauty (p.10).}

They claim that \paraphrase{the end result is a category of hybrid objects that bear the mark of at least two distinct domains, each with its won material, meaning, makers, and users (p.10).} (some of them utilitarian, some of them ornamental.) Whatever their ultimate function, each of these objects contains within itself a visual, material, and conceptual reference to multiple tehcnologies, histories and temporalities.

\quote{Like collage in art or quotation in literature, the recycled object carries a kind of "memory" of its prior existence. Recycling always implies a stance towrd time --- between the past nad the present --- and often a perspective on cultures --- one's own and others. (Jacknis 1992)}

\paraphrase{It is stated that same object can have one meaning for one community or culture and another meaning or series of meaninf for another. Different objects have different life spans --- different degrees of permanence or disposability --- and that these life spans are socially constituted is also an integrated part of the story \ldots geographic and socioeconomic boundaries of class, caste and culture throughout the world. It is story of people abour the women, men, children etc. one person's trash into another's treasure.}

\paraphrase{the process of refabrication explored here is not to be confused with the kind of industrial stregth recycling to which we in the West are most accustomed. When we think of recycling in America and other industrialized nations we imagine an autometed sequence begining with the curbside disposal of aluminum cans, plastic bottles, and old newspapers. returned to the industrial process. solid waste management, global greening, and ecological awareness are the buzzwords that guide and motivate consumers and industries to engage in this process of secondary and postconsumer waste recycling. }

There are different kinds of recycling that is small-scale, hand done, and local --- a kind of recycling in which yesterday's newspapers are transformed by hand into tin trunk liners;empty food cans become kerosene lanterns; and old tires are refashioned ... For the same people are not used the items that are scavenged by people who have little or no contact with those who first possessed them, and may neither know nor care about their originally intended function. It is case from the film and also the case depicted in the real life photographs taken by anthropologist michael leahy which document his first colonial contact with new guinean highlanders

(buraya yerlinin fotoğrafını koymak gerekli.)
“Renowned early-twentieth century anthropologist Michael Leahy encountered a Wabag man from Papua New Guinea wearing an aluminum whole wheat biscuit tin on his head. In the symbol system of this culture, large, bright, and shiny ornaments are connote health, well-being, sexual attractiveness, and the approval of the ancestors.

\paraphrase{We are dealing specifically with industrially produced consumer discards and their subsequent transformation, these essays are necessarily situated in a particular time, place, and sensibility: the consumer culture of the late twentieth century. In its most basic form, I refer to a consumer culture as one "in which the activities and ethics of a society are determined by patterns of consumption" rather than production (Mamiya 1992, 2)}

While consumption has provided a foundation for the transnatioal captitalist system adntheus has much longer history than the last fifty years this thesis focused on the more recent history. because it is during the history of consumption. comsumption can be though that as gloabal not to a western or first world countires.

It is not limited with geography, ethinicity, gender, nationaltiy. The process of of retrieving and trasnforming a consumer package or product that someone else has thrown away is a phenomenon that is taking place in the largest metropolises of urban america as well as the remotest corners of amazonian rain forest.

To frame a discussion that incorporates an understanding of such diverse locaions, objects, and peoples is to claim links between material process that originate under vastly different socail, economic, environmental, and political circumstances.

The most obvious link are the raw materials the raw materials themselves: the packaging, broken pieces. becomes raw materials for other things. these consumer items. and it is spreated globally. It can be seen remotest corner of the world. the indigenization of western objects. (sahlins, 16) Do these hybrid objects, as many western critics might assume, point to passive acceptance of a homogenized consumer culture in the service of western capitalist expansion, or, even worse, a sense of want and deprivation when confronted with "our riches"? Marshall Sahlins: "The first commercial impulse of the local people is not to become just like us, but more like themselves. They do not necessarily despise our commodities. But they are selective in their demands and transformative of their uses of such things. (sahlins, 13)"

human manufactured never envisioned possibilieties seen by people. It suggests a self-confididence and intellectual authority that allows local peoples to encompass western goods in their own meanings "in their own scheme of things."

This misuse the detritus of the industrial age has been described by western theorist as ironic. the irony is often embodied visually and conceptually. opposite of natural use, expected perception. for example making something from nothing or turning trash into treasure. By juxtaposing different materials changing context and place.

\quote{It is clear that one man's rubbish can be another man's desirable object; that rubbish, like beauty, is in the eye of the beholder. (thompson, 1979, 97)}

when an object is discarded it is perceived as being no longer of value to the person or society that once possessed it. Once a newspaper is read, or a bottle of soca pop consumed, its initial function is fulfilled and it is intended to be thrown aout as trash. .

Rubbish is, by definition, an object that is not or is no longer, owned by anyone, that falls outside all categories of economics, culture, and social control. As one of many things on the garbage heap, a discarded object even tends to take on a negative value as something unsanitary, dangerous. The socially constructed value of the object has shifted over time from its finite life span of usefulness and meaning to a timeless and valueless of socially sanctioned rubbish.

The remarkable thing about many of these objects - especially those produced in the last of the twentieth century - is that they were specifially designed to end up on the garbage heap. They were designed to decrease in value over time - to be used one, or twice and than to be thrown away. This applies not only applies packing - designed containers that protect and promote products - but to an ever expanding list of products. themselves. (Waste and wantta bununla ilgili bir bölüm olmalı.)

throwaway spirit (vance packard) Stephen jay gould has observed: "in our world of material wealth where so many broken items are thrown away "

The flip side of this paradigm is that a person's wealth has become measured not only in how much he or she can afford to consume, but in how much he or she can afford to throw away. America is one of the greatest country in terms of generating trash and exporting them to the other third world, fourt world countires. (bu ülkeler hangileri onları foot notte açıklayabilirsin.)

while most waste ends up in these unsanitary and unsightly landfills, some small percentage is reincorparated --- or recycled --- back into the economic and cultural system of the local population. Indeed, this is the power of rubbish as a category of possessable objects: it has within itself the potential of being discovered, retrieved, and trasnformed back into an object of greater or lesser durability.

If it is ultimately romantic to speak of these toys (or any other modern-day recyclia) in the language of resistance (by which I mean self-conscious political opposition), I would agree with Marshal Sahlins's assertion that "whether or not it comes to this [resistance], the indigenous mode of response to imperialism is always culturally subversive, insofar as the people must need to interpret the experiencei and they can do so only according to their own principles of existence. (sahlins 1992, 16)"

each recycled object contains within it a reference to two or more distinct times.

Whatever their ultimate design or destination, these recycled artifacts are, by definition, "impure", "inauthentic" products of past and present, here and there, "us" and "them" (clifford 1992)

recycling as an economic strategy of survival in develoing countries throughout the world. creative production that is motivated, primarily, by adverse conditions of economic necessity. (lanfill orchestra here. bookcovers here.) Economic survival and adaptation are influential factors for both the makers, who build informal business on the making and selling of recycled goods, and the local consumers, for whom the market for affordable, utilitarian goods is devised. (p25)

\subsection{Statistics:}
The United nations estimates that two percent of the people in cities in nonindustrialized countries make a living from the refuse discarded by the richest ten to twenty percent (germer 1991)
